---
title: "Assignment_0"
author: "Alexander Lopyrev"
date: "January 29, 2016"
output: html_document
---


In this assignment I am starting to practice R language.

I will do a few exercises to get a hang of it.

Github username: alopyrev

Link to the exercise source:

https://cran.r-project.org/doc/contrib/Torfs+Brauer-Short-R-Intro.pdf

#3. Some first exapmles of R


3.1 Calculator
```{r}
(2016-2014)/(2016-1992)*100
```

3.2 Workspace

```{r}
a = 2016

b = 2014

c = 1992

(a-b)/(a-c)*100
```

3.4 Functions

```{r}
sum(c(4,5,8,11))
```

3.5 Plots

```{r}
x = rnorm(100)

plot(x);
```


#4 HELP

```{r}
?sqrt
```

#5 Scripts
Made a file call "scripts_to_do.R"
```{r}
source("/home/alex/Desktop/Short_Intro_to_R/#5_Scripts_To_do.R")
```


#6 Vectors

6.2 Matrix+Vector

```{r}
P = seq(31,60)

Q = matrix(P, ncol=5, nrow=6 )

Q
```

6.3 Data Frames

```{r}
x1= rnorm(100)
x2= rnorm(100)
x3= rnorm(100)


t= data.frame(a= x1, b = (x1+x2),c = (x1+x2+x3))

t

plot(t)

sd(t$a)
sd(t$b)
sd(t$c)
```


#7 Graphics
```{r}
plot(t$a, type="l", ylim=range(t),
     lwd=3, col=rgb(1,0,0,0.3))
lines(t$b, type="s", lwd=2,
      col=rgb(0.3,0.4,0.3,0.9))
points(t$c, pch=20, cex=4, col=rgb(0,0,1,0.3))
```


The meaning of RGB is Red, Blue and Green. It determines the color of the markings on the graph.

#8 reading and writing from file
```{r}
r2 = read.table(file="tst1.txt", header=TRUE)
m= r2$g*5

write.table(m, file="tst2.txt")

```

9. Not available Data. Compute the mean of the sqrt of 100 random numbers

```{r}
sqrt(rnorm(100))
```

What happens? we get NaNs produced, NaN = not a number.



10.1 Make a graph with dates on X-Axis and presents on Y-Axis
```{r}
dates= strptime(c("20160127", "20160904","20161224"),format="%Y%m%d")
presents = c(0,7,5)

plot(dates,presents)
lines(dates,presents)
```

In the ToDo below I will make a vector from 1 to 100. Which will have a for-loop which runs through the wole vector. Elements that are smaller than 5 and larger than 90 will be mupltiplied by 10 and the other elements will be muliplied by 0.1

```{r}
hun = seq(from=1, to=100)
ss = c()

for(i in 1:length(hun)) 
{
  if(hun[i] < 5) {
    ss[i] <- (hun[i] *10)
  }else if (hun[i] > 90){
    ss[i] <- (hun[i] *10)
  }else{
    ss[i] = (hun[i]*0.1)
  }
}
ss;

```

This funciton is very similar to the for-loop above except you can provide your own argument for vector.

```{r}

fun1 = function(arg1)
{
  ss1=c()
  for(i in 1:length(arg1)) 
  {
    if(arg1[i] < 5) {
      ss1[i] <- (arg1[i] *10)
    }else if (hun[i] > 90){
      ss1[i] <- (arg1[i] *10)
    }else{
      ss1[i] = (arg1[i]*0.1)
    }
  }
  ss1
}


fun1(arg1=c(3:80))
```
